Yeast RNA-seq 48 sample simulation study

### 2018-04-05 datasets/RNA-Seq/yeast-simulation.Rmd
Fix typo in empirical comparison

# results on full set
dds <- DESeq(dds)
resultsNames(dds) # lists the coefficients
resFULL <- results(dds, name="condition_WT_vs_Snf2")

@@

sum(resFULL$padj < 0.05, na.rm=T, independentFiltering = F)
```

>>>>

# results on full set
dds <- DESeq(dds)
resultsNames(dds) # lists the coefficients
resFULL <- results(dds, name="condition_WT_vs_Snf2", independentFiltering = F)

@@

sum(resFULL$padj < 0.05, na.rm=T)
```
